### 2020-03-26 slides/preface.tex
Part I revised.
last change.

\begin{frame}[plain]{Disputation i Teknisk Mekanik}
\protect\hypertarget{disputation-i-teknisk-mekanik}{}
\note{The chair describes the procedure}

@@

\begin{longtable}[]{@{}rl@{}}
  \toprule
  \endhead
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Ordförande:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Prof.~Fredrik Lundell\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Respondent:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Zhouyang Ge\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Titel:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Droppinteraktioner och suspensionsflöden\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Handledare:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Prof.~Luca Brandt\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Assoc.~Prof.~Outi Tammisola\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Fakultetsopponent:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Assoc.~Prof.~Fran\c{c}ois Gallaire, École polytechnique fédérale de Lausanne, Schweiz\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Betygsnämnd:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Dr.~Elisabeth Lemaire, Institut de Physique de Nice, CNRS, Frankrike\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Assoc.~Prof.~Martin Trulsson, Lund Universitet, Sverige\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Dr.~Gustaf M\aa rtensson, Mycronic AB, Sverige\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Ersättare:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    Prof.~Shervin Bagheri, KTH, Sverige\strut
  \end{minipage}\tabularnewline
  \begin{minipage}[t]{0.22\columnwidth}\raggedleft
    \textbf{Sponsorer:}\strut
  \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
    EU Horizon 2020 (MICROFLUSA)\strut
  \end{minipage}\tabularnewline
  \bottomrule
\end{longtable}
\end{frame}

\begin{frame}[plain]{Procedure}
\protect\hypertarget{procedure}{}
\begin{itemize}
\item
  \textbf{The respondent will present the thesis}
  \medskip
\item
  \textbf{The opponent will discuss the thesis}
  \medskip
\item
  \textbf{The grading committee will ask questions}
  \medskip
\item
  \textbf{The audience may ask questions}
  \medskip
\item
  \textbf{The public part of the defence will be closed}
  \medskip
\item
  \textbf{The result will be announced at Osquars Backe 18, floor 6}
\end{itemize}
\end{frame}

>>>>

\begin{frame}[plain]{Disputation i Teknisk Mekanik (via länk)}
  \protect\hypertarget{disputation-i-teknisk-mekanik}{}
  \note{The chair describes the procedure}

  \begin{textblock}{12}(145,3)
    \includegraphics[width=\textwidth]{latex/kthgraphics/KTH-logo.pdf}
  \end{textblock}

@@

  \begin{longtable}[]{@{}rl@{}}
    \toprule
    \endhead

    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \textbf{Respondent:}\strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Zhouyang Ge\strut
    \end{minipage}\tabularnewline

    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \textbf{Titel:}\strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Droppinteraktioner och suspensionsflöden\strut
    \end{minipage}\tabularnewline

    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \textbf{Handledare:}\strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Prof.~Luca Brandt\strut
    \end{minipage}\tabularnewline

    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Assoc.~Prof.~Outi Tammisola\strut
    \end{minipage}\tabularnewline

    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \textbf{Fakultetsopponent:}\strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Assoc.~Prof.~Fran\c{c}ois Gallaire, École polytechnique fédérale de Lausanne, Schweiz\strut
    \end{minipage}\tabularnewline

    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \textbf{Betygsnämnd:}\strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Dr.~Elisabeth Lemaire, Institut de Physique de Nice, CNRS, Frankrike\strut
    \end{minipage}\tabularnewline
    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Assoc.~Prof.~Martin Trulsson, Lund Universitet, Sverige\strut
    \end{minipage}\tabularnewline
    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Dr.~Gustaf M\aa rtensson, Mycronic AB, Sverige\strut
    \end{minipage}\tabularnewline
    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \textbf{Ersättare:}\strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Prof.~Shervin Bagheri, KTH, Sverige\strut
    \end{minipage}\tabularnewline
    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \textbf{Sponsorer:}\strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      EU Horizon 2020 (MICROFLUSA)\strut
    \end{minipage}\tabularnewline

    \begin{minipage}[t]{0.22\columnwidth}\raggedleft
      \textbf{Ordförande:}\strut
    \end{minipage} & \begin{minipage}[t]{0.72\columnwidth}\raggedright
      Prof.~Fredrik Lundell\strut
    \end{minipage}\tabularnewline

    \bottomrule
  \end{longtable}
\end{frame}

\begin{frame}[plain]{Procedure}
  \protect\hypertarget{procedure}{}

  \begin{textblock}{12}(145,3)
    \includegraphics[width=\textwidth]{latex/kthgraphics/KTH-logo.pdf}
  \end{textblock}

  \begin{itemize}
  \item
    \textbf{The respondent will present the thesis online at the current meeting room}
    \medskip
  \item
    \textbf{The opponent will discuss the thesis with the respondent remotely via video}
    \medskip
  \item
    \textbf{The grading committee will ask questions remotely via video}
    \medskip
  \item
    \textbf{The audience may ask questions remotely (using the \emph{raise hand} feature)}
    \medskip
  \item
    \textbf{The public part of the defence will be temporarily closed}
    \medskip
  \item
    \textbf{The result will be announced online at the same meeting room}
  \end{itemize}

  \begin{textblock}{125}(14,79)
    \xr{\bf Please turn off your video and mute your microphone during the defence. Thank you.}
  \end{textblock}

\end{frame}
